\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-11-22 paper/mswp2012-proposal.tex
Trying to give the introduction a little bit more structure

Recent studies show that more and more people are getting obese these days due to an unhealthy lifestyle and way too less exercise, especially in the so called western society. Many studies and health reports in Europe and America describe the problem and show an increasing trend towards being overweight. The biggest problem in this area is that the situation is getting worse and worse. Especially children are rapidly becoming a big part of the problem, the risk of being an overweight child is about 30 percent, according to the Center for Disease Control \footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}. \\

Studies\citep{rki2012} show, that about 23 Percent of the people in Germany are obese nowadays. Being overweight affects your life in a lot of ways. From today's point of view overweight people are less attractive than others, have less success and and are more likely to be the victims of day-to-day discrimination \citep{carr05}. Moreover obesity can lead to very serious health problems like hypertension, asthma, diabetes and other cardiovascular problems.  \\

In the Forbes List for the fattest nation, Austria ranks on place 52 with a fat rate of 57.1\%.\footnote{\url{http://www.forbes.com/2007/02/07/worlds-fattest-countries-forbeslife-cx_ls_0208worldfat_3.html}}. Figure \ref{fig:obese_in_eu_pdf} shows a rather recent statistic of the situation in 25 European countries, divided by sex.

@@

One reason for the negative trend of childhood overweight are bad role models. Parents living an unhealthy lifestyle affect and influence their children. A recent study suggests that at-risk children are identifiable in their first years of life and tries to identify various risk factors \footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}. With increased age it gets harder to get in shape, the goal should be to teach children at young ages how to become and stay fit. In the future this negative trend will lead to an increased financial claim in our health care system - more and more people need expensive health treatments because of diseases caused by being obese over the years.  \\

@@

This project is accompanied by a scientific study. The goal of the study is to generate relevant data on which arrangements can motivate people the most and lead to best results as well as how people interact with a modern, technology-driven health care system, and how to improve these interactions. This data should lead to a good basis for future work on the topic. \\
% --------------------------------------------------------------
\section{Project goals and deliverables}
\label{sect:goals}

@@

The main hyphotesis to be investigated in this project is in the field of usability and ubiquitous computing. We want to generate knowledge on how a tracking system that monitors your whole day can be designed without being noticable and annoying. As already stated such a system can only succeed if the generation of useful data is as automized as possible, manual entries of exercices or nutrition facts can improve the data accuracy but shouldn't be vital for a working system.

>>>>

Recent studies show that more and more people are getting obese these days due to an unhealthy lifestyle and way too less exercise, especially in the so called western society. Many studies and health reports in Europe and America describe the problem and show an increasing trend towards being overweight. The biggest problem in this area is that the situation is getting worse and worse. Especially children are rapidly becoming a big part of the problem, the risk of being an overweight child in the US is about 30 percent - according to the Center for Disease Control \footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}. Another recent study suggests that at-risk children are identifiable in their first years of life and tries to identify various risk factors \footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}. \\

The situation in Europe isn't any better. European studies\citep{rki2012} show, that about 23 percent of the people living in Germany are obese nowadays. In the Forbes List for the fattest nation, Austria ranks on place 52 with a fat rate of 57.1\%.\footnote{\url{http://www.forbes.com/2007/02/07/worlds-fattest-countries-forbeslife-cx_ls_0208worldfat_3.html}}. Figure \ref{fig:obese_in_eu_pdf} shows a rather recent statistic of the situation in 25 European countries, divided by sex.

Being overweight affects your life in a lot of ways. From today's point of view overweight people are less attractive than others, have less success and and are more likely to be the victims of day-to-day discrimination \citep{carr05}. Moreover obesity can lead to very serious health problems like hypertension, asthma, diabetes and other cardiovascular problems.  \\

@@

One reason for the negative trend of childhood overweight are bad role models. Parents living an unhealthy lifestyle affect and influence their children. With increased age it gets harder to get in shape, the goal should be to teach children at young ages how to become and stay fit. In the future this negative trend will lead to an increased financial claim in our health care system - more and more people need expensive health treatments because of diseases caused by being obese over the years.  \\

@@

This project is accompanied by a scientific study. The goal of the study is to generate relevant data on which arrangements can motivate people the most and lead to best results as well as how people interact with a modern, technology-driven health care system and how to improve these interactions. The focus hereby is on the usability of an ubiquitous health tracking system that (half-)automatically generates useful data of the habits of the participants. This data should lead to a good basis for future work on the topic. \\
% --------------------------------------------------------------
\section{Project goals and deliverables}
\label{sect:goals}

@@

The main hyphotesis to be investigated in this project is in the field of usability and ubiquitous computing. We want to generate knowledge on how a tracking system that monitors your whole day can be designed without being noticable and annoying. As already stated such a system can only succeed if the generation of useful data is as automized as possible, manual entries of exercices or nutrition facts can improve the data accuracy but shouldn't be vital for a working system. \\
